NTM CT Scoring - Initial Agreement

### 2023-05-10 Stacey Martiniano/ntm_agreement.qmd
matched up gold standard IDs

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
# Select relevant columns, convert to long data
data <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id > 2) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6)
data <- data %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
data$location <- factor(data$location,
  levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", "lul", "rll", "rml", "rul"),
  labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
data$value <- factor(data$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
vals <- levels(data$value)
# One column per scorer
data <- data %>% pivot_wider(names_from = scorer, values_from = value)
# Find disagreements
data$disagree <- !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n <- length(vals)
name <- "Accent"
colors <- brewer.pal(n, name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
data$scan_id = as.numeric(data$scan_id)
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
# Revert duplicate IDs back to original to match with gold standard
training = read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/training.key.csv")
dups = read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/duplicated.key.csv")
data$scan_id[match(dups$duplicated_ssid..dates.shifted..17.days.,data$scan_id)] = dups$original_ssid
training$Training_id = as.numeric(sub("T00","",training$Training_id))
data$scan_id[data$scan_id %in% training$Training_id] <- 
  training$Cffid.Scoring.Set[match(data$scan_id, training$Training_id, nomatch = NA)]
# Select relevant columns, convert to long data
data <- data %>%
  arrange(scan_id, scorer) %>%
  filter(as.numeric(scan_id) <= 5) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6)
data <- data %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>% 
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
data$location <- factor(data$location,
  levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", "lul", "rll", "rml", "rul"),
  labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
data$value <- factor(data$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
vals <- levels(data$value)
# One column per scorer
data <- data %>% pivot_wider(names_from = scorer, values_from = value)
# Find disagreements
data$disagree <- !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n <- length(vals)
name <- "Accent"
colors <- brewer.pal(n, name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
# Get gold standard scores
gold_standard = read_excel("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Raw/gold_standard_scores.xlsx")
```
